Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2016-02-02 version1.0/manuscript.tex
sent to kipping
equation changes, a few more words. ready to resubmit

For our calibration data, we used a sample of \Kepler\ stars with
both asteroseismic and flicker measurements available. \citet{chaplin:2014}
report asteroseismic \rhostar\ estimates (and the associated uncertainties) for
518 \Kepler\ stars. The authors report three different sets of results,
depending on the choice of \Teff\ and \FeH, and in this work we elected to use
values reported in their Table 6 over Table 5, and Table 5 over Table 4. We
additionally used the 71 additional planet hosting stars with asteroseismology
reported in \citet{huber:2013} but not reported in \citet{chaplin:2014}. Values
for flicker and ``range'' were taken from \citet{kipping:2014}, based upon the
methods described in \citet{bastien:2013}. Following \citet{kipping:2014} and
for reasons described there-in, we only include targets in our calibration for
which:

@@

We used a likelihood function which accounts for 2-D uncertainties but does
not allow the intrinsic scatter to be a function of the dependent or
independent variables.
For the relation between flicker and \rhostar, this likelihood function can be
written as
\begin{eqnarray}
	& p(F_8|\rho_\star, \alpha, \beta, \sigma_{\rho}) \propto  \\ \nonumber
						      & \exp \left[-\frac{1}{2}
		\sum_{n=1}^N \frac{[F_{8n}-(\alpha + \beta \rho_{*n})]^2}
	{\left[\beta \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2
	+ \sigma_{\rho}^2\right]}\right]
	\\ \nonumber
	& + \beta^2 \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2 + \sigma_{\rho}^2,
\end{eqnarray}
\label{eq:likelihood}
and similarly for \logg.
We found that the posterior PDFs for the model parameters obtained using this
likelihood function were consistent with those obtained using a model that
only accounts for the uncertainties on the flicker measurements.
Accounting for uncertainties on $y$ {\it and} $x$ is therefore not essential
in this case but still good practise and will, in general, produce more
accurate model parameters and uncertainties.

@@

We used the uninformative prior for the parameters of a straight line for
data with unknown uncertainties, outlined in \citet{vanderplas},
\begin{equation}
P(\alpha, \beta, \sigma) \propto \frac{1}{\sigma} \left( 1 + \beta^2
\right)^{-3/2}.
\end{equation}
\label{eq:priors}

@@

Figures \ref{fig:rhostar} and \ref{fig:logg} show the data with the best-fit
models.
The shaded regions show the 1 and 2$\sigma$ confidence interval which are
representative of the intrinsic scatter in the relations.
% Given a measurement of flicker, the predictive probability distribution of
% \logg and \rhostar will be a Gaussian distribution

%%% rhostar plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{flicker_vs_rho.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/rho_vs_flicker.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{new_rho.pdf}
\caption{
Stellar density vs. flicker.
This figure shows the model, conditioned on the data.
The solid black line shows the model with the parameter values quoted in the
text.
The solid pink lines show the 1$\sigma$ region where the extra scatter is not
included and the pink shaded regions show the 1 and 2$\sigma$ regions with the
additional scatter.}
\label{fig:rhostar}
\end{center}
\end{figure}

%%% logg plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{flicker_vs_logg.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/logg_vs_flicker.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{new_logg.pdf}
\caption{
$\log(g)$ vs. flicker.
As in \ref{fig:rhostar} this figure shows the model, conditioned on the data.
The solid black line shows the model with the parameter values quoted in the
text.
The solid blue lines show the 1$\sigma$ region where the extra scatter is not
included and the blue shaded regions show the 1 and 2$\sigma$ regions with the
additional scatter.}
\label{fig:logg}
\end{center}
\end{figure}

>>>>

For our calibration data, we used a sample of \Kepler\ stars with
both asteroseismic and flicker measurements available. \citet{chaplin:2014}
report asteroseismic \rhostar\ estimates (and the associated uncertainties) for
518 \Kepler\ stars. The authors report three different sets of results,
depending on the choice of \Teff\ and \FeH, and in this work we elected to use
values reported in their Table 6 over Table 5, and Table 5 over Table 4. We
additionally used the 71 additional planet hosting stars with asteroseismology
reported in \citet{huber:2013} but not reported in \citet{chaplin:2014}. Values
for flicker and ``range'' were taken from \citet{kipping:2014}, based upon the
methods described in \citet{bastien:2013}.
% Following \citet{kipping:2014} and
% for reasons described there-in, we only include targets in our calibration for
% which:
In order to use the same data set as \citet{kipping:2014} and
for reasons described there-in, we only include targets in our calibration for
which:

@@

We used a likelihood function which accounts for 2-D uncertainties but does
not allow the intrinsic scatter to be a function of the dependent or
independent variables.
For the relation between flicker and \rhostar, this likelihood function can be
written as
\begin{eqnarray}
	& p(F_8|\rho_\star, \alpha_\rho, \beta_\rho, \sigma_{\rho}) \propto  \\ \nonumber
						      & \exp \left[-\frac{1}{2}
		\sum_{n=1}^N \frac{[F_{8n}-(\alpha_\rho + \beta_\rho \rho_{*n})]^2}
	{\left[\beta_\rho \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2
	+ \sigma_{\rho}^2\right]}\right]
	\\ \nonumber
	& + \beta_\rho^2 \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2 + \sigma_{\rho}^2,
\end{eqnarray}
\label{eq:likelihood}
and similarly for \logg.
We found that the posterior PDFs for the model parameters obtained using this
likelihood function were consistent with those obtained using a model that
only accounts for the uncertainties on the flicker measurements.
Accounting for uncertainties on $y$ {\it and} $x$ is therefore not essential
in this case but still good practise and will, in general, produce more
accurate model parameters and uncertainties.

@@

We used the uninformative prior for the parameters of a straight line for
data with unknown uncertainties, outlined in \citet{vanderplas},
\begin{equation}
p(\alpha, \beta, \sigma) \propto \frac{1}{\sigma} \left( 1 + \beta^2
\right)^{-3/2}.
\end{equation}
\label{eq:priors}

@@

We also tested flat priors and found that the results were insensitive to this
choice.
Figures \ref{fig:rhostar} and \ref{fig:logg} show the data with the best-fit
models.
The shaded regions show the 1 and 2$\sigma$ confidence interval which are
representative of the intrinsic scatter in the relations.
% Given a measurement of flicker, the predictive probability distribution of
% \logg and \rhostar will be a Gaussian distribution

%%% rhostar plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{flicker_vs_rho.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/rho_vs_flicker.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{new_rho.pdf}
\caption{
Stellar density vs. flicker.
This figure shows the model, conditioned on the data.
The solid black line shows the model with the best-fitting parameter values
quoted in the text.
The solid pink lines show the 1$\sigma$ region where the extra scatter is not
included and the pink shaded regions show the 1 and 2$\sigma$ regions with the
additional scatter.}
\label{fig:rhostar}
\end{center}
\end{figure}

%%% logg plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{flicker_vs_logg.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/logg_vs_flicker.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{new_logg.pdf}
\caption{
$\log(g)$ vs. flicker.
As in \ref{fig:rhostar} this figure shows the model, conditioned on the data.
The solid black line shows the model with the best-fitting parameter values
quoted in the text.
The solid blue lines show the 1$\sigma$ region where the extra scatter is not
included and the blue shaded regions show the 1 and 2$\sigma$ regions with the
additional scatter.}
\label{fig:logg}
\end{center}
\end{figure}
